---
title: 'bobross'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
knitr::opts_knit$set(root.dir="~/Documents/ncssm")
```

Dataset from https://github.com/jwilber/Bob_Ross_Paintings pulled from https://www.twoinchbrush.com/

some stuff here talking about it. use tidyverse functions because dataset not big and syntax is more human-readable. but don't show code most of the time

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(purrr)
library(stringr)
library(mvtnorm)
```


```{r}
bob <- read_csv("./data/Bob_Ross_Paintings/data/bob_ross_paintings.csv") %>%
  mutate(color_hex = str_replace_all(color_hex, "[\\[\\s\\]']", "") %>% 
           str_split(., ","),
         # uppercase hex causes problems for ggplot2, incorrect colors based on testing
         color_hex = map(color_hex, tolower),
         colors = str_replace_all(colors, "[\\[\\]']|\\\\r|\\\\n", "") %>% 
           str_split(., ",", simplify=F),
         colors = map(colors, str_trim))
#head(bob)
```

comments about rows and columns, observations and variables, things and types of things


section on what we are trying to do

- plot points of colors used in a painting
- summarize color use by season

```{r}
make_cloud <- function(p, n, spread, sigmasq){
  cloud <- lapply(p, FUN = function(x) {
    out <- rmvnorm(n, mean = c(runif(1, min = -spread, max = spread), 
                               runif(1, min = -spread, max = spread)),
                   sigma = sigmasq*diag(2))
    colnames(out) <- c('x', 'y')
    as_tibble(out)
  })
  names(cloud) <- p
  
  cloud
}

make_blob <- function(p, n, spread){
  blob <- lapply(p, FUN = function(x) {
    tibble(x = runif(1, min = -spread, max = spread), y = runif(1, min = -spread, max = spread))
  })
  
  blob
}
#for later plotting params
spread <- 8
bob <- mutate(bob, cloud = map(colors, make_cloud, n = 1000, spread = spread, sigmasq = 10),
                   blob = map(colors, make_blob, n = 1000, spread = spread))
```

What are the colors in this painting?

```{r}
painting <- sample_n(bobsmall, 1)
paste("Painting:", painting$painting_title)
paste("Season, episode:", painting$season, ",", painting$episode)
paste("Youtube:", painting$youtube_src)
#for debugging color
#paste(painting$color_hex[[1]])
#paste(painting$colors[[1]])
```

```{r, dpi=800}
knitr::include_graphics(painting$img_src)
```

Image courtesy of https://www.twoinchbrush.com/

Let's plot the colors in a random point cloud


```{r, dpi=800}
bind_rows(painting$cloud[[1]], .id='color') %>%
  ggplot(aes(x, y, color = color)) + geom_point(alpha = .5) +
  theme_void() + scale_color_manual(values = painting$color_hex[[1]])
```


```{r, dpi=800}
blobd <- bind_rows(painting$blob[[1]], .id='color') %>% mutate(color = painting$colors[[1]])

ggplot(blobd, aes(x, y, color = color)) + geom_point(alpha = .5, size = 5*spread) +
  theme_void() + scale_color_manual(values = painting$color_hex[[1]]) +
  theme(legend.position="none") +
  annotate('text', x = blobd$x, y = blobd$y,
           label = blobd$color, size = 3, color = 'grey20') +
  xlim(-1.3*spread, 1.3*spread) + ylim(-1.3*spread, 1.3*spread)
```


plot several point clouds side by side in facets, by painting name

summary of color use by season, in table and graph format


short walkthrough 'how I got the data', mostly conceptual and introduces the idea of git
