---
title: ''
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
knitr::opts_knit$set(root.dir="~/Documents/ncssm")
```


Propub work on restraints and seclusion (forced isolation) in public schools

Using dataset that is regularly update, latest release:
https://www.ed.gov/news/press-releases/us-department-education-releases-2017-18-civil-rights-data-collection


an example of:

- publicly released government data
- on a serious issue
- with a codebook
- citizenship through data science

```{r}
library(data.table)
setDTthreads(2)
```


```{r}
d <- fread("./data/restraints_propub/public-use-files-2017-18/Data/SCH/CRDC/CSV/Restraint and Seclusion.csv")
d <- d[, .(state = LEA_STATE, LEAID, SCHID, TOT_RS_NONIDEA_MECH_M, TOT_RS_NONIDEA_MECH_F,
           TOT_RS_NONIDEA_SECL_M, TOT_RS_NONIDEA_SECL_F, TOT_RS_NONIDEA_PHYS_M, TOT_RS_NONIDEA_PHYS_F)]
```

What is this garbage? Why negatives?
```{r}
dsum <- d[, 
          .(male_mech = sum(TOT_RS_NONIDEA_MECH_M), 
            female_mech = sum(TOT_RS_NONIDEA_MECH_F), 
            male_secl = sum(TOT_RS_NONIDEA_SECL_M),
            female_secl = sum(TOT_RS_NONIDEA_SECL_F),
            male_phys = sum(TOT_RS_NONIDEA_PHYS_F),
            female_phys = sum(TOT_RS_NONIDEA_PHYS_F)), 
          by = state]
```

LOOK AT PUERTO RICO OH MY GOD

reformat to make prettier
```{r}
barplot(-dsum$male_mech, names.arg = dsum$state, 
        cex.names = 0.5, horiz = F, las=2, col = "wheat3",
        main = "Male students subject to mechanical restraint, '17-'18",
        sub = "", xpd = F) # reformat --- sub gets in way of plot xpd not doing what I thought
```

```{r}
barplot(-dsum$male_secl, names.arg = dsum$state, 
        cex.names = 0.5, horiz = F, las=2, col = "tomato3",
        main = "Male students subject to seclusion, '17-'18",
        sub = "", xpd = F) # reformat --- sub gets in way of plot xpd not doing what I thought
```


whats the deal 
```{r}
barplot(as.matrix(-dsum[, .(male_mech, male_secl)]), beside = T,
        cex.names = 0.5, horiz = F, las=2, col = c("wheat3", "tomato3"),
        main = "Male students subject to mech. restraint/seclusion, '17-'18",
        sub = "", xpd = F) # reformat --- sub gets in way of plot xpd not doing what I thought
```

groupwise summaries by gender(M/F) and state for non-disability students subjected to seclusion and mechanical or physical restraint in school
maybe a simple map

do this with base R as much as possible

so many resources and examples! eg
https://www.r-graph-gallery.com/

little section on how I got the data, understanding the variables etc
data quality problems --- this will be common!